$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-05-21 paper/Referee-response.tex

\documentclass[12pt]{article}
\usepackage{fullpage}
\begin{document}
\noindent Dear editor,
\\

\noindent Thank you for sending us the referee report.  We would like to
sincerely thank the referee for their very helpful comments and questions
about our paper.  In response to each of these we have made appropriate
changes to our manuscript and feel these have improved the paper.  We
therefore hope that our paper will now be considered acceptable for
publication in Physical Review D.
\\
\noindent We respond to each point raised by the referee below, explaining
where appropriate what changes we have made in the paper to address the
referee's concerns.

### 2015-05-21 paper/e6ssm-tuning-paper.tex
Corrected minor typos

A number of alternative measures have also been applied in the
literature \cite{Anderson:1994dz, Anderson:1994tr, Anderson:1995cp,
Anderson:1996ew, Ciafaloni:1996zh, Chan:1997bi, Barbieri:1998uv,
Giusti:1998gz, Casas:2003jx, Casas:2004uu, Casas:2004gh,
Casas:2006bd, Kitano:2005wc, Athron:2007ry, Athron:2007qr,
Baer:2012up} with varying motivations.  A very different approach is
to work within a Bayesian analysis.  There the concept of naturalness
is automatically incorporated since in models where one must fine tune
parameters to fit measured values of the observables, the region with
high likelihood will occupy a tiny prior volume \cite{Allanach:2007qk,
Cabrera:2008tj, Ghilencea:2012gz, Ghilencea:2012qk, Fichet:2012sn,
Kim:2013uxa} suppressing the posterior.  Indeed in the MSSM and
the next-to-MSSM (NMSSM) if one transforms GUT scale parameters to the
VEVs, the inverse of the Jacobian for this transformation looks quite like
the derivatives that appear in the traditional fine tuning measure
\cite{Allanach:2007qk, Cabrera:2008tj, Kim:2013uxa}.  If one thinks
more generally then a model without fine tuning is one where the
parametrization is such that all the parameters are observables
\cite{Fichet:2012sn, Kim:2013uxa}.  This provides a quite general
definition of fine tuning as $1/|J|$ where $|J|$ is the determinant of
the Jacobian for the co-ordinate transformation between the parameters
and the observables.  Interestingly this means the tuning is the ratio
of the infinitesimal observable space space volume element to the
infinitesimal parameter space element and coincides with the measure
proposed in \cite{Athron:2007ry} when the interval of variation is
taken to zero.

@@

However if the extra $U(1)$ gauge symmetries appears from the
breakdown of $E_6$, then $\sin\chi$ should be zero at the GUT scale.
Nonetheless even if this term is zero at the outset it will still be
radiatively generated if the trace of their charges, $\sum_i Q_i^Y
Q^\prime_i$, is non-zero.  In the cases studied here the trace of the
charges over states in the complete $27$-plets vanish, but to be
consistent with single step gauge coupling unification we also
included $\hat{H}^\prime$ and $\hat{\overline{H^\prime}}$ which lead
to a non-zero value for $\sum_i Q_i^Y Q^\prime_i $.  The value induced
by this at the EW scale though is rather small as can be
seen\footnote{The specific incomplete multiplets we consider here
  correspond to the third of the four possible embeddings they refer
  to.} in Fig.~3 of \cite{Rizzo:1998ut}, and this was also checked
with two-loop RGEs in the E$_6$SSM \cite{King:2005jy,Athron:2009bs}.
For this reason and due to the huge expansion in the number of terms
in the two-loop RGEs when one allows for gauge kinetic mixing we will
neglect this in our analysis here and throughout this paper.

@@

As discussed in the introduction many recent papers interested in
natural supersymmetry have focussed on light stops, with much
theoretical effort to find models where it is easier to get a $125$
GeV Higgs boson and light stops simultaneously and much experimental
effort to search for light stops.  This is entirely appropriate since
there are many good reasons to expect the soft masses to be set at
high energies.  However that is not the only possibility and the fine
tuning problem depends strongly on the RG evolution from the GUT
scale, as the soft Higgs masses that appear in the EWSB conditions
pick up contributions from the soft squark masses.

>>>>

A number of alternative measures have also been applied in the
literature \cite{Anderson:1994dz, Anderson:1994tr, Anderson:1995cp,
Anderson:1996ew, Ciafaloni:1996zh, Chan:1997bi, Barbieri:1998uv,
Giusti:1998gz, Casas:2003jx, Casas:2004uu, Casas:2004gh,
Casas:2006bd, Kitano:2005wc, Athron:2007ry, Athron:2007qr,
Baer:2012up} with varying motivations.  A very different approach is
to work within a Bayesian analysis.  There the concept of naturalness
is automatically incorporated since in models where one must fine tune
parameters to fit measured values of the observables, the region with
high likelihood will occupy a tiny prior volume \cite{Allanach:2007qk,
Cabrera:2008tj, Ghilencea:2012gz, Ghilencea:2012qk, Fichet:2012sn,
Kim:2013uxa} suppressing the posterior.  Indeed in the MSSM and
the next-to-MSSM (NMSSM) if one transforms GUT scale parameters to the
VEVs, the inverse of the Jacobian for this transformation looks quite like
the derivatives that appear in the traditional fine tuning measure
\cite{Allanach:2007qk, Cabrera:2008tj, Kim:2013uxa}.  If one thinks
more generally then a model without fine tuning is one where the
parameterization is such that all the parameters are observables
\cite{Fichet:2012sn, Kim:2013uxa}.  This provides a quite general
definition of fine tuning as $1/|J|$ where $|J|$ is the determinant of
the Jacobian for the co-ordinate transformation between the parameters
and the observables.  Interestingly this means the tuning is the ratio
of the infinitesimal observable space space volume element to the
infinitesimal parameter space element and coincides with the measure
proposed in \cite{Athron:2007ry} when the interval of variation is
taken to zero.

@@

However if the extra $U(1)$ gauge symmetries appears from the
breakdown of $E_6$, then $\sin\chi$ should be zero at the GUT scale.
Nonetheless even if this term is zero at the outset it will still be
radiatively generated if the trace of their charges, $\sum_i Q_i^Y
Q^\prime_i$, is non-zero.  In the cases studied here the trace of the
charges over states in the complete $27$-plets vanish, but to be
consistent with single step gauge coupling unification we also
included $\hat{H}^\prime$ and $\hat{\overline{H^\prime}}$ which lead
to a non-zero value for $\sum_i Q_i^Y Q^\prime_i $.  The value induced
by this at the EW scale though is rather small as can be
seen\footnote{The specific incomplete multiplets we consider here
  correspond to the third of the four possible embeddings referred to in
  Ref.~\cite{Rizzo:1998ut}.} in Fig.~3 of Ref.~\cite{Rizzo:1998ut}, and this
was also checked
with two-loop RGEs in the E$_6$SSM \cite{King:2005jy,Athron:2009bs}.
For this reason and due to the huge expansion in the number of terms
in the two-loop RGEs when one allows for gauge kinetic mixing we will
neglect this in our analysis here and throughout this paper.

@@

As discussed in the introduction many recent papers interested in
natural supersymmetry have focused on light stops, with much
theoretical effort to find models where it is easier to get a $125$
GeV Higgs boson and light stops simultaneously and much experimental
effort to search for light stops.  This is entirely appropriate since
there are many good reasons to expect the soft masses to be set at
high energies.  However that is not the only possibility and the fine
tuning problem depends strongly on the RG evolution from the GUT
scale, as the soft Higgs masses that appear in the EWSB conditions
pick up contributions from the soft squark masses.
